TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-07 paper/draft.tex
atmospheres

\color{gcolor}Why is there a problem determining M dwarf metallicities (and especially for high res \apogee\ spectra)? Emphasize issues: (1) models dont accurately reproduce data; (2) empirical standards are relative not absolute, and they are sparesely sampled. 
Methods for determining metallicity of M dwarfs: (1) from atmospheric models of M dwarfs, (2) empirical methods: photometric calibrations (\citealt{Johnson:2009}; \citealt{Schlaufman:2010}) or spectroscopic calibrations (\citealt{Terrien:2012}; \citealt{Rojas-Ayala:2012}; \citealt{Mann:2013a}; \citealt{Newton:2014}) with FGK pairs. Our approach is the latter.\color{black}

>>>>

While elemental abundance measurements from high resolution spectra of F, G, and K stars have achieved extremely high precisions (down to errors in the range of $0.01-0.03$\,dex; \citealt{Nissen2018}) enabled by the improvement of atmospheric models (citations),
the determination of precise metallicities for M dwarfs has remained a long standing challenge, due to the formation of complex molecular features at temperatures, particularly TiO and VO which dominate the optical, H$_2$O and CO which dominate the infrared, and hydride molecules (FeH, CaH, CrH, MgH, etc.) which form at late spectral types \citep{Allard1997}.
